
---
title: "Introduction to mfcurve"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to mfcurve}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# mfcurve: Multi-Factor Curve Analysis in R

## Overview

`mfcurve` is an R package designed for analyzing multi-factor models, similar to the Stata `mfcurve` ado file. It provides functions for preprocessing data, conducting statistical tests, and generating visualizations to explore group differences in mean outcomes with confidence intervals.

## Installation

To install the package from GitHub, you can use the following commands:

```{r, eval = FALSE}
# Install devtools if not already installed
install.packages("devtools")

# Install mfcurve package from GitHub
devtools::install_github("cweileder/mfcurve")
```

## Key Features

- **Preprocessing**: Filter missing values, handle factors, and create groups.
- **Statistical Testing**: Conduct statistical tests (e.g., t-tests) on group means to flag significant differences.
- **Visualization**: Generate visualizations showing group differences with confidence intervals.

## Example Usage

### 1. Preprocessing Data

```{r, eval = FALSE}
# Load necessary libraries
library(mfcurve)
library(dplyr)

# Sample data
data <- data.frame(
  wage = c(10, 20, 30, 40, 15, 25, 35, 45),
  race = factor(c("black", "black", "white", "white", "black", "white", "black", "white")),
  union = factor(c(1, 0, 1, 0, 1, 0, 1, 0))
)

# Preprocess the data
preprocessed_data <- mfcurve_preprocessing(data, "wage", c("race", "union"))

# View the preprocessed data
print(preprocessed_data)
```

### 2. Conducting Statistical Tests

```{r, eval = FALSE}
# Conduct statistical tests
test_results <- mfcurve_stat_test(preprocessed_data, level = 0.05, test = "mean")

# View the test results
print(test_results)
```

### 3. Plotting the Results

```{r, eval = FALSE}
# Plot the results
mfcurve_plot(test_results)
```

## Contributing

Contributions are welcome! Please fork this repository and submit a pull request with your changes.

## License

This package is licensed under the MIT License - see the [LICENSE](LICENSE) file for details.
